Dependent Object Types

### 2012-07-01 doc/semester/report.tex
rev

@@

@@

\section{Counterexamples}

@@

\section{Patches}

@@

First, path reduction is not isomorphic to reduction anymore, since we
actually want to actually skip over widenings, as motivated by the
last example in~\ref{widening}.

@@

Notice that $d$ has type $\Bot$ if you ginore the cast on $b$. This
example doesn't typecheck initially because $\textsc{path-$\sub$}$
only applies when objects are in the store, so the application is not
well-typed. But if we start preservation in a store which has $a$,
$b$, $c$ and $d$ then the application type-checks, because, through
$\textsc{path-$\sub$}$, we can find that the type of $d$ is a subtype
of $\Bot$. Now, of course, when we get to $d.\mathit{foo}$, reduction
fails.

@@

\section{Conclucion and Future Work}

>>>>

DOT models Scala's path-dependent types and abstract type members, as
well as its mixture of nominal and structural typing through the use
of refinement types. It makes no attempt to model inheritance or
mixing composition. The calculus does not model what's currently in
Scala: it is more normative than descriptive.

@@

In the rest of this introduction, we present some program examples. We
summarize our findings of counterexamples to soundness in
section~\ref{counterexs}. We explore some patches to the calculus in
section~\ref{patches}. We discuss opportunities for future work and
conclude in section~\ref{conclusion}.

@@

\section{Counterexamples}\label{counterexs}

@@

\section{Patches}\label{patches}

@@

First, path reduction is not isomorphic to reduction anymore, since we
want to actually skip over widenings, as motivated by the last example
in~\ref{widening}.

@@

Notice that $d$ has type $\Bot$ if you ignore the cast on $b$. This
example doesn't typecheck initially because $\textsc{path-$\sub$}$
only applies when objects are in the store, so the application is not
well-typed. But if we start preservation in a store which has $a$,
$b$, $c$ and $d$ then the application type-checks, because, through
$\textsc{path-$\sub$}$, we can find that the type of $d$ is a subtype
of $\Bot$. Now, of course, when we get to $d.\mathit{foo}$, reduction
fails.

@@

\section{Conclucion and Future Work}\label{conclusion}
This semester's work was instructive in pointing out the problematic
aspects of the original DOT calculus, and exploring some possible
fixes. However, I haven't been able to reach a revised calculus
without soundness hole. Furthermore, I believe that the revised
calculus with all the patches is not as elegant as the original
calculus. Going forward, I want to take a broader view by by studying
and incorporating ideas from other calculi which models dependent
types, and path-dependent types in particular.
